---
title: "hw3"
format: html
editor: visual
---

## Task 1: Conceptual Questions

1.  If your working directory is myfolder/homework/, what relative path would you specify to get the file located at myfolder/MyData.csv?

"../MyData.csv"

2.  What are the major benefits of using R projects?

3.  What is git and what is github?

4.  What are the two main differences between a tibble and a data.frame?

5.  Rewrite the following nested function call using baseR’s chaining operator: arrange(filter(select(as_tibble(iris), starts_with("Petal"), Species), Petal.Length \< 1.55), Species)

6.  What is meant by long format data and wide format data? Which do we generally prefer for statistical analysis?

## Task 2 Reading Delimited Data

1.  

```{r}
library(tidyverse)
```

```{r}
glass <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/glass.data",
                  col_names = c("Id", "RI", "Na", "Mg", "Al", "Si","K","Ca","Ba","Fe","Type_of_Glass"))
glass
```

2.  

```{r}
glass<- glass %>%
  mutate(Type_of_Glass1 = case_when(
    Type_of_Glass == 1 ~ "building_windows_float_processed",
    Type_of_Glass == 2 ~ "building_windows_non_float_processed",
    Type_of_Glass == 3 ~ "vehicle_windows_float_processed",
    Type_of_Glass == 4 ~ "vehicle_windows_non_float_processed",
    Type_of_Glass == 5 ~ "containers",
    Type_of_Glass == 6 ~ "tableware",
    Type_of_Glass == 7 ~ "headlamps"
  ))

glass
```

3.  

```{r}
glass_filtered <- glass %>%
  filter(Fe < 0.2 & (Type_of_Glass1 == "tableware" | Type_of_Glass1 == "headlamps"))
glass_filtered
```
