---
title: "hw3"
format: html
editor: visual
---

## Task 1: Conceptual Questions

1.  If your working directory is myfolder/homework/, what relative path would you specify to get the file located at myfolder/MyData.csv?

"../MyData.csv"

2.  What are the major benefits of using R projects?

3.  What is git and what is github?

4.  What are the two main differences between a tibble and a data.frame?

5.  Rewrite the following nested function call using baseR’s chaining operator: arrange(filter(select(as_tibble(iris), starts_with("Petal"), Species), Petal.Length \< 1.55), Species)

6.  What is meant by long format data and wide format data? Which do we generally prefer for statistical analysis?

## Task 2 Reading Delimited Data
### Glass data
1.  

```{r}
library(tidyverse)
```

```{r}
glass <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/glass.data",
                  col_names = c("Id", "RI", "Na", "Mg", "Al", "Si","K","Ca","Ba","Fe","Type_of_Glass"))
glass
```

2.  

```{r}
glass<- glass |>
  mutate(Type_of_Glass1 = case_when(
    Type_of_Glass == 1 ~ "building_windows_float_processed",
    Type_of_Glass == 2 ~ "building_windows_non_float_processed",
    Type_of_Glass == 3 ~ "vehicle_windows_float_processed",
    Type_of_Glass == 4 ~ "vehicle_windows_non_float_processed",
    Type_of_Glass == 5 ~ "containers",
    Type_of_Glass == 6 ~ "tableware",
    Type_of_Glass == 7 ~ "headlamps"
  ))

glass
```

3.  

```{r}
glass_filtered <- glass |>
  filter(Fe < 0.2 & (Type_of_Glass1 == "tableware" | Type_of_Glass1 == "headlamps"))
glass_filtered
```
### Yeast data
1.
```{r}
yeast <- read_table("https://www4.stat.ncsu.edu/~online/datasets/yeast.data",
                  col_names = c("seq_name", "mcg", "gvh", "alm", "mit", "erl","pox","vac","nuc","class"))
yeast
```
2.
```{r}
yeast_s<- yeast|>
  select(-c(seq_name, nuc))
yeast_s
```
3.
```{r}
yeast_d<- yeast|>
  select(-c(seq_name, nuc))|>
  group_by(class)|>
  mutate(across(c(mcg, gvh, alm, mit, erl, pox, vac), 
                list(mean = ~ mean(.), median = ~ median(.)),
                .names = "{.col}_{.fn}"))

yeast_d
```

## Task 2: Combining Excel and Delimited Data
 1. 
```{r}
library(readxl)
library(dplyr)
```

```{r}
white_wine <- read_excel("white-wine.xlsx", 
                            sheet = excel_sheets("white-wine.xlsx")[1])
white_wine
```

2. 
```{r}
white_wine2 <- read_excel("white-wine.xlsx", 
                            sheet = excel_sheets("white-wine.xlsx")[2])
white_wine2
```
```{r}
white_wine3 <- read_excel("white-wine.xlsx", sheet = excel_sheets("white-wine.xlsx")[1])

colnames(white_wine3) <- c("fixed_acidity", "volatile_acidity", "citric_acid", "residual_sugar", 
                           "chlorides", "free_sulfur_dioxide", "total_sulfur_dioxide", 
                           "density", "pH", "sulphates", "alcohol", "quality")
white_wine3
```
3
```{r}
white_wine4 <- white_wine3 |>
  mutate(wine = 1)
```

